---
title: 'Experimental Economics: Data Workflow'
author: 
  - Matteo Ploner\inst{1}
institute: 
  - \inst{1} DEM-CEEL, University of Trento
date-format: long
# title-slide-attributes:
#     # data-background-color: "#eb820a"
format:
    html:
        embed-resources: true
        toc: true
        theme: Cyborg 
editor: visual
editor_options:
  markdown:
    wrap: 55
---

## Course Description

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=6, fig.align="center", dpi=300}
library(DiagrammeR)
```

The course deals with the design of an experiment in social sciences and the management of the related data workflow . As a take-home assignment, participants are invited to develop their own experimental design and implement the related software.

The following chart illustrates the workflow of the course.

```{r echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, fig.align="center"}

#| label: workflow
#| fig-cap: "Workflow"

grViz("
      digraph contents {

graph [compound = true, rankdir = LR, layout = dot, bgcolor= black]

node[fontname = Helvetica, fontcolor = black, shape = rounded, fixedsize = true, width = 1.2, style = filled, fillcolor = Honeydew, fontsize = 8]

'Design'
'Registration'
'Programming'
'Data collection'
'Data organization'


'Design' -> 'Registration' 
'Registration' -> 'Programming'
'Programming' -> 'Data collection'
'Data collection' -> 'Data organization'

node[fontname = Helvetica, fontcolor = black, shape = oval, style = filled, fontsize = 8, fixedsize = false, fillcolor = white]

'Methodology'
'oTree'
'OSF'
'Prolific'

'Methodology' -> 'Design' [arrowhead = none, color=grey78]
'OSF' -> 'Registration' [arrowhead = none, color=grey78]
oTree -> 'Programming'[arrowhead = none, color = grey78]
Prolific -> 'Data collection'[arrowhead = none, color = grey78]
'Render' -> 'Data collection'[arrowhead = none, color = grey78]
'R (tidyverse)' -> 'Data organization'[arrowhead = none, color = grey78]


subgraph cluster_0 {
        graph[shape = rectangle]
        style = filled
        fontcolor= white
        fontname = Helvetica
        fillcolor = DeepSkyBlue
        label = 'GitHub'
        
node[fontname = Helvetica, fontcolor = black, shape = oval, color = darkslategray, style=filled, fillcolor = LemonChiffon, fontsize=10, fixedsize = true,  width=1.5]
      'Design'
      'Registration'
      'Programming'
      'Data collection'
      'Data organization'
        
}

}
      ",
    width = "100%",
    height = "100%"
)
```

- Design
    - Methodological aspects of the design of an economic experiments are discussed in the classroom

- Registration
    - Illustration of the pre-registration process on [OSF](https://osf.io/){target="_blank"} with specific attention to hypotheses and data analysis

- Programming
    - Introduction to [oTree](https://www.otree.org/){target="_blank"} architecture and examples of experimental apps

- Data collection
    - Recruitment of participants via [Prolific](https://www.prolific.co/){target="_blank"} and online deployment on [render.com](https://render.com/){target="_blank"}

- Data organization
    - Collection, organization  and documentation of data in [R](htpps://cran.r-project.org){target="_blank"}


## Modules

### 1) Methodology

#### Introduction

[SLIDES](./1/INTRO_printout.html){target="_blank"}

### Methdology of Experimental Economics

[SLIDES](./1/METHOD_printout.html){target="_blank"}

### 2) oTree: Programming and management of online experiments

[SLIDES](./2/SLIDES.html){target="_blank"}

[CODE](./2/CODE.zip){target="_blank"}

### 3) oTree: Individual decision making and strategic games

[SLIDES](./3/SLIDES.html){target="_blank"}

[CODE](./3/CODE.zip){target="_blank"}

### 4) oTree: Sequential games

[SLIDES](./5/slidesTG_printout.html){target="_blank"}

[CODE](./5/CODE/TG.zip){target="_blank"}

### 5) oTree: Style

[SLIDES](./5/slidesADV_printout.html){target="_blank"}

[CODE](./5/CODE/styles.zip){target="_blank"}

### 6) R: Data wrangling

[SLIDES](./6/SLIDES_printout.html){target="_blank"}

[DATA](./6/DATA.zip){target="_blank"}

### 7) R: Document creation

[SLIDES](./7/R_presentation_printout.html){target="_blank"}

[DEMO Report](./7/Report.zip){target="_blank"}

### 8) oTree: online deployment 

[SLIDES](./7/oTree_deployment_printout.html){target="_blank"}


<script src="https://code.iconify.design/3/3.1.0/iconify.min.js"></script>