---
title: "Experimental Economics: Data Workflow"
subtitle: "Syllabus"
author: "Matteo Ploner (DEM-CEEL,University of Trento, Italy)"
date: "21 February 2023"
date-format: long
title-slide-attributes:
    data-background-color: "#547980"
    data-background-size: contain
    data-background-opacity: "0.8"
editor: visual
theme: lumen
#bibliography: ./bib.bib
editor_options:
  markdown:
    wrap: 72
---

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=6, fig.align="center", dpi=300}
library(DiagrammeR)
```

## Description

The course deals with the design of an experiment in social sciences and the management of the related data workflow . As a take-home assignment, participants are invited to develop their own experimental design and implement the related software.

The following chart illustrates the workflow of the course.

```{r echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, fig.align="center"}

#| label: workflow
#| fig-cap: "Workflow"

grViz("
      digraph contents {

graph [compound = true, rankdir = LR, layout = dot]

node[fontname = Helvetica, fontcolor = black, shape = rounded, fixedsize = true, width = 1.2, style = filled, fillcolor = Honeydew, fontsize = 8]

'Design'
'Registration'
'Programming'
'Data collection'
'Data organization'


'Design' -> 'Registration' 
'Registration' -> 'Programming'
'Programming' -> 'Data collection'
'Data collection' -> 'Data organization'

node[fontname = Helvetica, fontcolor = black,  shape=oval, style=empty, fontsize = 8, fixedsize = false]

'Methodology'
'oTree'
'OSF'
'Prolific'

'Methodology' -> 'Design' [arrowhead = none]
'OSF' -> 'Registration' [arrowhead = none]
oTree -> 'Programming' [arrowhead = none]
Prolific -> 'Data collection' [arrowhead = none]
'Render' -> 'Data collection' [arrowhead = none]
'R (tidyverse)' -> 'Data organization'[arrowhead = none]


subgraph cluster_0 {
        graph[shape = rectangle]
        style = filled
        fontcolor= white
        fontname = Helvetica
        fillcolor = DeepSkyBlue
        label = 'GitHub'
        
        node[fontname = Helvetica, fontcolor = black, shape = oval, color = darkslategray, style=filled, fillcolor = LemonChiffon, fontsize=10, fixedsize = true,  width=1.5]
      'Design'
      'Registration'
      'Programming'
      'Data collection'
      'Data organization'
        
}

}
      ",
    width = "100%",
    height = "100%"
)
```

- Design
    - Methodological aspects of the design of an economic experiments are discussed in the classroom

- Registration
    - Illustration of the pre-registration process on [OSF](https://osf.io/) with specific attention to hypotheses and data analysis

- Programming
    - Introduction to [oTree](https://www.otree.org/) architecture and examples of experimental apps

- Data collection
    - Recruitment of participants via [Prolific](https://www.prolific.co/) and online deployment on [render.com](https://render.com/)

- Data organization
    - Collection, organization  and documentation of data in [R](htpps://cran.r-project.org)

## Prerequisites

- Basic knowledge of experimental economics.
- Basic knowledge of computer programming.
- Access to a computer.
  - Installation of [o-Tree software](https://www.otree.org/) (open source and free of charge).
  - Installation of [R software](htpps://cran.r-project.org) (open source and free of charge) and [R Studio](https://www.rstudio.com/) (open source and free of charge).


## Calendar

| Lecture  | Day  | Hour | Room | Topic|
|---|---|---|---|--|
| [1](./1/)  | 27/03  | 09:00-12:00 |Lab4 |Inro and Methodology |
| 2  | 06/04  | 09:00-12:00 |Lab4 |oTree: Programming and management of experiments in oTree |
| 3  | 11/04  | 09:00-12:00 |Lab1 |oTree: Fundamental components of an experiment|
| 4  | 18/04  | 09:00-12:00 |Lab1 |Design of an experiment (Laboratory)|
| 5  | 27/04  | 09:00-12:00 |Lab4 |oTree: Questionnaires and individual decision making|
| 6  | 02/05  | 09:00-12:00 |Lab4 |oTree: Strategic interaction|
| 7  |  09/05 | 09:00-12:00 |Lab4 |R: Data organization |
| 8  | 30/05  | 09:00-12:00 |Lab4 |Projects' presentation + online implementation|

## Evaluation

Students are asked to develop an experimental project in oTree. The project will be evaluated in terms of software functioning and originality.

## Contacts

Matteo Ploner<br>

<span class="iconify" data-icon="ri:building-4-line"></span>
 Department of Economics and Management, University of Trento <br>
Via Inama 5 <br>
38123 Trento (Italy) <br>

<span class="iconify" data-icon="material-symbols:mail-outline-rounded"></span>
 [matteo.ploner@unitn.it](mailto: matteo.ploner@unitn.it)

<span class="iconify" data-icon="mdi:web"></span>
[https://matteoploner.eco.unitn.it](https://matteoploner.eco.unitn.it)

<script src="https://code.iconify.design/3/3.1.0/iconify.min.js"></script>
